A Procedure for the Rapid Processing and Georeferencing of Hyperspectral Imagery for Real-Time use by an Autonomous Aerial Vehicle

### 2023-09-22 paper/draft.qmd
more updates

@@

In our previous work, we demonstrated a prototype autonomous robot team employing a drone based hyper-spectral imager which can learn the mapping from reflectance spectra to concentrations of variety of chemicals-of-concern by utilizing the information contained in the reflectance spectra captured with a HSI  [@robot-team-1]. In this paper, we present a procedure based on the method of [@muller-georeferencing] for the rapid processing and georeferencing of imagery captured by a pushbroom HSI mounted on an autonomous. Associated code can be freely accessed and downloaded in (**add reference to our repository**)

>>>>

The increased spectral resolution of HSI systems poses unique challenges to their adoption for real time applications primarily stemming from the considerable size of generated data files. Current data collection workflows see researchers first perform the aerial survey (data collection) and then transfer data to ground based computers for post processing. This workflow is well established in the remote sensing community where, as an example, compressed raw imagery from Sentinel-2 are transferred to the ground and then subsequently post processed into their final L1C (top of atmosphere) and L2A (bottom of atmosphere) data products ((**add citation here**)). Drone based applications often operate in a similar manner: images or video are collected by a survey and then post-processed and analyzed with software such as Open Drone Map to produce the desired data products (tile mosaics, 3d reconstructions, etc.) (**add citation**). For an HSI platform to function in real time, three key computational tasks are critical: 
1. **FileIO**: captured imagery need to be quickly read by the on-board processing computer
2. **Post-processing**: Raw imagery need to be rapidly converted to the chosen data product (typically, Reflectance), and importantly, must be georeferenced so that each image pixel can be located on the ground.
3. **Ground Transfer**: Sufficient wireless communication must be avaiable to transmit the final

The first can be readily accomplished by means of light weight, high volume solid state drives. To address the second, we need both sufficient compute and optimized processing software. Finally, ground transfer of final post-processed data products can be accomplished in a variety of ways. As we rarely need the full hyper-spectral datacube right away, once can generate the desired data products on board (NDVI for example) and transfer only the relevant information to a ground station

@@

In our previous work, we demonstrated a prototype autonomous robot team employing a drone based hyper-spectral imager which can learn the mapping from reflectance spectra to concentrations of variety of chemicals-of-concern by utilizing the information contained in the reflectance spectra captured with a HSI together with a  [@robot-team-1]. In this paper, we present a procedure based on the method of [@muller-georeferencing] for the rapid processing and georeferencing of imagery captured by a pushbroom HSI mounted on an autonomous. Associated code can be freely accessed and downloaded in (**add reference to our repository**)
